Gammapy: A Python package for gamma-ray astronomy

### 2023-06-15 src/ms-review.tex

\subsection{DL3: Events And Instrument Response Functions}
An overview of the typical steps in the high level analysis is shown in the upper
row of Figure~\ref{fig:data_flow}. The high level analysis starts at the DL3 
data level, where \gammaray data is represented as lists of \gammaray-like events and their
corresponding IRFs $R$ and ends at the DL5/6 data level, where the physicallyy relevant 
quantities such as fluxes, spectra and light curves of sources have been derived. DL3 data are typically 
bundled into individual observations, corresponding to
stable periods of data acquisition. For IACT instruments, for which the \gadf
data model and \gammapy were initially conceived, this duration is typically 
$t_{\rm obs}=15 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
The event list is just a simple table with one event per row and
the measured event properties as columns. These properties e.g., include reconstructed
incident direction and energy, arrival time and reconstruction quality.

>>>>

\subsection{DL3: Events And Instrument Response Functions}
An overview of the typical steps in the high level analysis is shown in the upper
row of Figure~\ref{fig:data_flow}. The high level analysis starts at the DL3 
data level, where \gammaray data is represented as lists of \gammaray-like events and their
corresponding IRFs $R$ and ends at the DL5/6 data level, where the physically relevant 
quantities such as fluxes, spectra and light curves of sources have been derived. DL3 data are typically 
bundled into individual observations, corresponding to
stable periods of data acquisition. For IACT instruments, for which the \gadf
data model and \gammapy were initially conceived, this duration is typically 
$t_{\rm obs}=15 - 30\,{\rm min}$. Each observation is assigned a unique integer ID for reference.
The event list is just a simple table with one event per row and
the measured event properties as columns. These properties e.g., include reconstructed
incident direction and energy, arrival time and reconstruction quality.
